Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-07-12 2016-Weak-FH-Bisim/WeakBisim.tex
in proof of lemma 7
proof of lemma 7 OK

\usepackage[T1]{fontenc}
%\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{a4paper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{DotArrow}

@@

\begin{lemma}
\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  The two following statements are equivalent
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
\begin{enumerate}
\item Either $   
\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
there exist   $\set{\beta_{1i}}$, $\set{\beta_{2i}}$, and $\set{\beta_{3i}}$, $\Pred_{1i}$, $\Pred_{3i}$, $\Post_{1i}$, and  $\Pred_2$, $\Post_2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [0..n].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0..m].\openrule
         {
           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}    }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}
 \end{mathpar}
\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha'} s'} \in\WT
%}
\end{mathpar}
where\\
$
\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n}^{0}\Post_j^1}}\\
s=s_{10} \wedge s_{1(n+1)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
\displaystyle{
\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
\\
\Pred=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}
$

@@

\[Q\models{\openrule
	{
		\set{\beta_2},
		 \Pred_2,  
		\Post_2}
	{\ostate{s_{20}}\OTarrow {\alpha_Q}
		\ostate{s_{21}}}
}
\]

@@

such that 
$s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\

@@

By Lemma \ref{lem-rel-OT-WOT} from cases $(1)$, $(2)$ and $(3)$ we obtain: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
\set{\gamma'}, \Pred_c,
\Post_c}
         {\ostate{s_{10}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha} 
	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
where
\[\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta_{1h}}} \dotcup \vis{{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta_{3h}}}\]
\[
\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_i^1}\land
\left(Pred\land\Pred_2\land \alpha_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\\displaystyle
\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
\end{array}
\]

@@

Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on state variables of $Q$. A
\end{proof}

>>>>

\usepackage[T1]{fontenc}
%\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{a4paper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{DotArrow}
\usepackage{hyperref}

@@

\begin{lemma}
\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  The two following statements are equivalent
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
\begin{enumerate}
\item Either $   
\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
there exist   $\set{\beta_{1i}}$, $\set{\beta_{2i}}$, and $\set{\beta_{3i}}$, $\Pred_{1i}$, $\Pred_{3i}$, $\Post_{1i}$, and  $\Pred_2$, $\Post_2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [0..n].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0..m].\openrule
         {
           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}    }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}
 \end{mathpar}
\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha'} s'} \in\WT
%}
\end{mathpar}
where\\
$
\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n}^{0}\Post_{1j}}}\\
s=s_{10} \wedge s_{1(n+1)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
\displaystyle{
\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
\\
\Pred=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}
$

@@

\[Q\models{\openrule
	{
		\set{\beta_2},
		 \Pred_2,  
		\Post_2}
	{\ostate{s_{20}}\OTarrow {\alpha'_Q}
		\ostate{s_{21}}}
}
\]

@@

such that 
$\alpha_Q=\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$\\
$s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\

@@

By Lemma \ref{lem-rel-OT-WOT} from cases $(1)$, $(2)$ and $(3)$ we obtain: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
\set{\gamma'}, \Pred_c,
\Post_c}
         {\ostate{s_{10}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha'} 
	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
where
\[\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}} \]
and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$

\[\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta_{1h}}} \dotcup \vis{{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta_{3h}}}=\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}\]
\[
\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_i{1i}}\land
\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\\displaystyle
\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
\end{array}
\]

@@

Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on state variables of $Q$. We conclude on predicate and posts as follows\footnote{$\Post_{1i}$ only has an effect on variables of $Q$ and thus does not modify $\Pred$ or $\beta_{j_0}$}:
\begin{equation*}
\begin{split}
\Pred_c&=\Pred_Q\land\Pred\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land
(\alpha'_Q=\beta_{j_0})subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\\
&=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\Post_c&=\Post\uplus\Post_Q
\end{split}
\end{equation*}
\qed
\end{proof}
